Will it blend: Is the Milky Way bar causing chaotic fanning of the Ophiuchus stream?

### 2015-08-14 ms.tex
adding more section outlines

The Ophiuchus stream \citep{bernard14} is located in an interesting region of the Milky Way. Many streams have been found in the halo at Galactocentric distances of XX--YY kpc, but Ophiuchus is situated near the Galactic center where the gravitational potential should have significant components from the bulge and bar of the Milky Way. Recent modeling fit for the orbit, found discrepancy between dynamical age and age of stellar populations \citep{sesar15}, however they assume an axisymmetric disk plus spherical bulge and halo. If the Galactic bar contributes significantly to the density distribution of the inner Galaxy, the orbit of the cluster could be entirely different.

@@

@@

The three-dimensional shape and density distribution of the inner galaxy is not well known.

>>>>

* Observational work on the stream (Bernard, Sesar)

@@

* Summarize chaos work

* Why is Ophiuchus interesting?

- Shortness of the stream

- Possible fanned debris

- Discrepancy between dynamical / stellar population age of the stream

The Ophiuchus stream is located in a unique position relative to other known stellar tidal streams: Many streams have been found in the halo of the Milky Way at Galactocentric distances of XX--YY kpc. For this stream, it is therefore expected that the baryonic components of the Milky Way---the combination of the bulge, disk, and Galactic bar---should dominate the kinematic history of the progenitor system. Unfortunately, the density distribution or gravitational potential of the inner Galaxy is not well known.

Recent modeling fit for the orbit, found discrepancy between dynamical age and age of stellar populations \citep{sesar15}, however they assume an axisymmetric disk plus spherical bulge and halo. If the Galactic bar contributes significantly to the density distribution of the inner Galaxy, the orbit of the cluster could be entirely different.

Our goal is to assess whether the Galactic bar can produce significant numbers of chaotic orbits in the inner Galaxy and see if the Ophiuchus stream could plausibly be on a strongly chaotic orbit. If chaos is important for this stream, we would then like to show that chaotic stream-fanning can reproduce the observed morphology and velocity signatures of ... In this section, we describe the methods we will use to detect and quantify the strength of chaos for orbits and then explain the method we will use to generate mock tidal streams.

@@
